---
title: "GulfCorals"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#Packages used throughout document:
library(plyr)
library(readr)
library(ggplot2)
library(GGally)
library(dplyr)
library(mlbench)
```

#For first look, going to work with genus-level IDs at specific depth ranges of interest.
First, need to determine best way to sort out the area we are interested in. Potential location identifies: 
  'Ocean': Interested in "North Atlantic", but still larger than wanted
  'FishCouncilRegion': Interested in "South Atlantic" and "Gulf of Mexico"
  'Locality': Probably too specific
  'Country': Interested in "USA" "Mexico", but council regions preferred 

```{r}
AllData <- read.csv("C:/Users/17572/Desktop/AllData.csv")
glimpse(AllData)
```

```{r}
Cat56L2<- read.csv("C:/Users/17572/Desktop/Cat56L2.csv")
View(Cat56L2)
```

```{r}
#Which of the 4 locality identifies have missing values?
head(apply(Cat56L2,2,anyNA))
#All values present for 'Ocean', other three categories have missing data (represented as 'NA')
```

```{r}
#What proportion of the data in each column is 'NA'?
  #Total number of rows = 791907
  colSums(is.na(Cat56L2))
```

#Percent of data available for use in each category:
  'Ocean': (791907/791907)*100 = 100%
  'FishCouncilRegion': ((791907-26444)/791907)*100 = 96.66%
  'Locality': ((791907-59246)/791907)*100 = 92.52%
  'Country': ((791907-122108)/791907)*100 = 84.58%
  
#'FishCouncilRegion' will be used to filter the data for the remainder of this exercise

```{r}
Cat56L<- read.csv("C:/Users/17572/Desktop/Cat56L.csv")
View(Cat56L)
```

```{r}
glimpse(Cat56L)
```

```{r}
#What proportion of the data in each column is 'NA'?
  #Total number of rows = 791907
  colSums(is.na(Depth2))
```

```{r}
#Filter large data set to include only samples from the "South Atlantic" and "Gulf of Mexico" Fish Council Regions
Regions<-c("Gulf of Mexico","South Atlantic")
Cat56<-Cat56L %>% filter(FishCouncilRegion==Regions)
glimpse(Cat56)
```

```{r}
#Start by filtering for the desired depth range, as "DepthInMeters" is already an 'int' value
Depth1<-Cat56 %>% filter(30<=DepthInMeters)
Depth2<-Depth1 %>% filter(DepthInMeters<=300)
summary(Depth2$DepthInMeters)
glimpse(Depth2)
#Check that the min and max displayed in the summary are the same as those specified above
```

```{r}
#
Swiftia<-Depth2 %>% filter(Genus=="Swiftia")
glimpse(Swiftia)
```

#There are 754 records of Genus Swiftia in the Gulf of Mexico/South Atlantic, between 30 and 300m of depth to work with for the rest of the analysis

##Starting over with big data set

```{r}
#Which of the 4 locality identifies have missing values?
head(apply(AllData,2,anyNA))
#All values present for 'Ocean', other three categories have missing data (represented as 'NA')
```

```{r}
#What proportion of the data in each column is 'NA'?
  #Total number of rows = 791907
  colSums(is.na(AllData))
```

#Percent of data available for use in each category:
  'Ocean': (791907/791907)*100 = 100%
  'FishCouncilRegion': ((791907-26444)/791907)*100 = 96.66%
  'Locality': ((791907-59246)/791907)*100 = 92.52%
  'Country': ((791907-122108)/791907)*100 = 84.58%
  
#'FishCouncilRegion' will be used to filter the data for the remainder of this exercise

```{r}
Cat56L<- read.csv("C:/Users/17572/Desktop/Cat56L.csv")
View(Cat56L)
```

```{r}
glimpse(Cat56L)
```

```{r}
#What proportion of the data in each column is 'NA'?
  #Total number of rows = 791907
  colSums(is.na(Depth2))
```

```{r}
#Filter large data set to include only samples from the "South Atlantic" and "Gulf of Mexico" Fish Council Regions
Regions<-c("Gulf of Mexico","South Atlantic")
AllDataRegions<-AllData %>% filter(FishCouncilRegion==Regions)
glimpse(AllDataRegions)
```

#Swiftia, Thesia, and Muricea: 30-300m Depth Range 

```{r}
#Depth limits
Depth3<-AllDataRegions %>% filter(30<=DepthInMeters)
Depth4<-Depth3 %>% filter(DepthInMeters<=300)
summary(Depth4$DepthInMeters)
glimpse(Depth4)
#Check that the min and max displayed in the summary are the same as those specified above
```

```{r}
ScientificNames<-subset(AllDataRegions, select=c(ScientificName))
View(ScientificNames)
freq<-sapply(ScientificNames, function(x) table(factor(x, levels=ScientificNames$SceintificName, order=TRUE)))
print(freq)
```
```{r}
#All names included in data base with frequencies
table(AllData['ScientificName'])
#All names included in GOM and South Atlantic, 30-300m, with frequencies 
table(Depth4['ScientificName'])
#All names included in GOM and South Atlantic, 1000-3000m, with frequencies 
table(Depth6['ScientificName'])
```


```{r}
#Now location and depth range have been determined, so combine all swiftia of interest in the 'ScientificName' field
Swiftia1<-Depth4 %>% filter(ScientificName=="Swiftia")
SwiftiaCasta<-Depth4 %>% filter(ScientificName=="Swiftia casta")
SwiftiaExserta<-Depth4 %>% filter(ScientificName=="Swiftia exserta")
SwiftiaKoreni<-Depth4 %>% filter(ScientificName=="Swiftia koreni")
#Combine all occurrences into the final "Swiftia" Data Set:
Swiftia<-rbind(Swiftia1,SwiftiaCasta,SwiftiaExserta,SwiftiaKoreni)
glimpse(Swiftia)
```

```{r}
SwiftiaCasta<-Depth4 %>% filter(ScientificName=="Swiftia casta")
glimpse(SwiftiaCasta)
```

```{r}
SwiftiaExserta<-Depth4 %>% filter(ScientificName=="Swiftia exserta")
glimpse(SwiftiaExserta)
```

```{r}
SwiftiaKoreni<-Depth4 %>% filter(ScientificName=="Swiftia koreni")
glimpse(SwiftiaKoreni)
```

```{r}
#Combine all occurrences into the final "Swiftia" Data Set:
Swiftia<-rbind(Swiftia1,SwiftiaCasta,SwiftiaExserta,SwiftiaKoreni)
glimpse(Swiftia)
```

```{r}
#Now do the same for Thesea
Thesea1<-Depth4 %>% filter(ScientificName=="Thesea")
glimpse(Thesea1)
```

```{r}
TheseaCFCitrina<-Depth4 %>% filter(ScientificName=="Thesea cf. citrina")
glimpse(TheseaCFCitrina)
```

```{r}
TheseaSolitaria<-Depth4 %>% filter(ScientificName=="Thesea solitaria")
glimpse(TheseaSolitaria)
```

```{r}
Thesea<-rbind(Thesea1, TheseaCFCitrina, TheseaCFGuadalupensis, TheseaCFHebes, TheseaCFParviflora, TheseaCitrina, TheseaGrandiflora, TheseaGranulosa, TheseaNivea, TheseaNutans, TheseaParviflora, TheseaPlana, TheseaRubra, TheseaRugosa, TheseaSolitaria)
glimpse(Thesea)
```

```{r}
#Muricea
Muricea1<-Depth4 %>% filter(ScientificName=="Muricea")
glimpse(Muricea1)
```

```{r}
HypnogorgiaPendula<-Depth4 %>% filter(ScientificName=="Hypnogorgia pendula")
glimpse(HypnogorgiaPendula)
```

```{r}
Muricea<-rbind(Muricea1, MuriceaPendula, HypnogorgiaPendula)
glimpse(Muricea)
```


#Paramuricea: 1000-3000m Depth Range 

```{r}
#Depth limits
Depth5<-AllDataRegions %>% filter(1000<=DepthInMeters)
Depth6<-Depth5 %>% filter(DepthInMeters<=3000)
summary(Depth6$DepthInMeters)
glimpse(Depth6)
#Check that the min and max displayed in the summary are the same as those specified above
```

```{r}
ParamuriceaPlacomus<-Depth6 %>% filter(ScientificName=="Paramuricea placomus")
glimpse(ParamuriceaPlacomus)
```

```{r}
Paramuricea<-rbind(Paramuricea1, ParamuriceaBiscaya)
glimpse(Paramuricea)
```

#Now what percent of each category has usable data within these 4 groups of interest?

```{r}
AllGroups<-rbind(Swiftia, Thesea, Muricea, Paramuricea)
glimpse(AllGroups)
```

```{r}
colSums(is.na(AllGroups))
```

```{r}
summary(AllGroups$OperationalTaxonomicUnit)
```

```{r}
MinimumSize<-AllGroups %>% filter(-999.00<MinimumSize)
glimpse(MinimumSize)
```

```{r}
GroupPercents <- read.csv("C:/Users/17572/Desktop/GroupPercents.csv")
 View(GroupPercents)
```


```{r}
colnames(GroupPercents)[1]<-"FieldName"
Rank6<-GroupPercents %>% filter(Rankings==6)
Rank5<-GroupPercents %>% filter(Rankings==5)
Rank4<-GroupPercents %>% filter(Rankings==4)
Rank3<-GroupPercents %>% filter(Rankings==3)
Rank2<-GroupPercents %>% filter(Rankings==2)
Rank1<-GroupPercents %>% filter(Rankings==1)
Rank0<-GroupPercents %>% filter(Rankings==0)
```

```{r}
#Rank 6 categories
ggplot(data=Rank6, aes(x=reorder(FieldName, +Percent.Usable.Data), y=Percent.Usable.Data, fill=FieldName)) +
  geom_bar(stat="identity")+
  geom_text(aes(label=Percent.Usable.Data), vjust=0.5, hjust=1.5, color="black", size=3.5)+
  theme(legend.position = "none", plot.title=element_text(hjust=0.5))+
  coord_flip()+
  labs(title="NOAA Deep Sea Coral Data Portal:\nRank 6 Field of Interest Percent Completion", x="Field Name", y="Percent of Field Filled (%)")
```

```{r}
#Rank 5 categories
ggplot(data=Rank5, aes(x=reorder(FieldName, +Percent.Usable.Data), y=Percent.Usable.Data, fill=FieldName)) +
  geom_bar(stat="identity")+
  geom_text(aes(label=Percent.Usable.Data), vjust=0.5, hjust=1.5, color="black", size=3.5)+
  theme(legend.position = "none", plot.title=element_text(hjust=0.5))+
  coord_flip()+
  labs(title="NOAA Deep Sea Coral Data Portal:\nRank 5 Field of Interest Percent Completion", x="Field Name", y="Percent of Field Filled (%)")
```

```{r}
#Rank 4 categories
ggplot(data=Rank4, aes(x=reorder(FieldName, +Percent.Usable.Data), y=Percent.Usable.Data, fill=FieldName)) +
  geom_bar(stat="identity")+
  geom_text(aes(label=Percent.Usable.Data), vjust=0.3, hjust=1.5, color="black", size=2.5)+
  theme(legend.position = "none", plot.title=element_text(hjust=0.5))+
  coord_flip()+
  labs(title="NOAA Deep Sea Coral Data Portal:\nRank 4 Field of Interest Percent Completion", x="Field Name", y="Percent of Field Filled (%)")
```

```{r}
#Rank 3 categories
ggplot(data=Rank3, aes(x=reorder(FieldName, +Percent.Usable.Data), y=Percent.Usable.Data, fill=FieldName)) +
  geom_bar(stat="identity")+
  geom_text(aes(label=Percent.Usable.Data), vjust=0.3, hjust=1.5, color="black", size=2.5)+
  theme(legend.position = "none", plot.title=element_text(hjust=0.5))+
  coord_flip()+
  labs(title="NOAA Deep Sea Coral Data Portal:\nRank 3 Field of Interest Percent Completion", x="Field Name", y="Percent of Field Filled (%)")
```

```{r}
#Rank 2 categories
ggplot(data=Rank2, aes(x=reorder(FieldName, +Percent.Usable.Data), y=Percent.Usable.Data, fill=FieldName)) +
  geom_bar(stat="identity")+
  geom_text(aes(label=Percent.Usable.Data), vjust=0.4, hjust=1.5, color="black", size=3.5)+
  theme(legend.position = "none", plot.title=element_text(hjust=0.5))+
  coord_flip()+
  labs(title="NOAA Deep Sea Coral Data Portal:\nRank 2 Field of Interest Percent Completion", x="Field Name", y="Percent of Field Filled (%)")
```

```{r}
#Rank 1 categories
ggplot(data=Rank1, aes(x=reorder(FieldName, +Percent.Usable.Data), y=Percent.Usable.Data, fill=FieldName)) +
  geom_bar(stat="identity")+
  geom_text(aes(label=Percent.Usable.Data), vjust=0.4, hjust=1.5, color="black", size=3.5)+
  theme(legend.position = "none", plot.title=element_text(hjust=0.5))+
  coord_flip()+
  labs(title="NOAA Deep Sea Coral Data Portal:\nRank 1 Field of Interest Percent Completion", x="Field Name", y="Percent of Field Filled (%)")
```

```{r}
#Rank 0 categories
ggplot(data=Rank0, aes(x=reorder(FieldName, +Percent.Usable.Data), y=Percent.Usable.Data, fill=FieldName)) +
  geom_bar(stat="identity")+
  geom_text(aes(label=Percent.Usable.Data), vjust=0.5, hjust=1.5, color="black", size=3.5)+
  theme(legend.position = "none", plot.title=element_text(hjust=0.5))+
  coord_flip()+
  labs(title="NOAA Deep Sea Coral Data Portal:\nRank 0 Field of Interest Percent Completion", x="Field Name", y="Percent of Field Filled (%)")
```

```{r}
#Percent Completion, including all groups 0 < % Completion < 100
GreaterThan0<-GroupPercents %>% filter(0<Percent.Usable.Data)
LessThan100<-GreaterThan0 %>% filter(Percent.Usable.Data<100)
summary(LessThan100$Percent.Usable.Data)
```

```{r}
#All ranks, percent completions >0 and <100
ggplot(data=LessThan100, aes(x=reorder(FieldName, +Percent.Usable.Data), y=Percent.Usable.Data, fill=factor(Rankings))) +
  geom_bar(stat="identity")+
  geom_text(aes(label=Percent.Usable.Data), vjust=0.5, hjust=1.5, color="black", size=3.5)+
  theme(plot.title=element_text(hjust=0.5))+
  coord_flip()+
  labs(title="NOAA Deep Sea Coral Data Portal:\nFields of Interest Percent Completion", x="Field Name", y="Percent of Field Filled (%)")+
  scale_fill_discrete(guide = guide_legend(reverse=TRUE), name="Ranking")
```
```{r}
#Percent Completion, split in half by percentage
GreaterThan50<-LessThan100 %>% filter(50<Percent.Usable.Data)
LessThan50<-LessThan100 %>% filter(Percent.Usable.Data<50)
summary(GreaterThan50$Percent.Usable.Data)
summary(LessThan50$Percent.Usable.Data)
```
```{r}
#All ranks, greater than 50%
ggplot(data=GreaterThan50, aes(x=reorder(FieldName, +Percent.Usable.Data), y=Percent.Usable.Data, fill=factor(Rankings))) +
  geom_bar(stat="identity")+
  geom_text(aes(label=Percent.Usable.Data), vjust=0.35, hjust=1.2, color="black", size=3)+
  theme(plot.title=element_text(hjust=0.5))+
  coord_flip()+
  labs(title="NOAA Deep Sea Coral Data Portal:\nFields of Interest, 50-99% Completion", x="Field Name", y="Percent of Field Filled (%)")+
  scale_fill_discrete(guide = guide_legend(reverse=TRUE), name="Ranking")
```
```{r}
#All ranks, less than 50%
ggplot(data=LessThan50, aes(x=reorder(FieldName, +Percent.Usable.Data), y=Percent.Usable.Data, fill=factor(Rankings))) +
  geom_bar(stat="identity")+
  geom_text(aes(label=Percent.Usable.Data), vjust=0.35, hjust=1.2, color="black", size=2.9)+
  theme(plot.title=element_text(hjust=0.5))+
  coord_flip()+
  labs(title="NOAA Deep Sea Coral Data Portal:\nFields of Interest, 1-49% Completion", x="Field Name", y="Percent of Field Filled (%)")+
  scale_fill_discrete(guide = guide_legend(reverse=TRUE), name="Ranking")
```
```{r}
#Grouping ranks 6-4 and 3-0
Rank54<-rbind(Rank5,Rank4)
Rank32<-rbind(Rank3,Rank2)
Rank10<-rbind(Rank1,Rank0)
#Percent Completion, including all groups 0 < % Completion < 100
GreaterThan0a<-Rank54 %>% filter(0<Percent.Usable.Data)
LessThan100a<-GreaterThan0a %>% filter(Percent.Usable.Data<100)
summary(LessThan100a$Percent.Usable.Data)
GreaterThan0b<-Rank32 %>% filter(0<Percent.Usable.Data)
LessThan100b<-GreaterThan0b %>% filter(Percent.Usable.Data<100)
summary(LessThan100b$Percent.Usable.Data)
GreaterThan0c<-Rank10 %>% filter(0<Percent.Usable.Data)
LessThan100c<-GreaterThan0c %>% filter(Percent.Usable.Data<100)
summary(LessThan100b$Percent.Usable.Data)
```
```{r}
#Ranks 4-5, >0% and <100%
ggplot(data=LessThan100a, aes(x=reorder(FieldName, +Percent.Usable.Data), y=Percent.Usable.Data, fill=factor(Rankings))) +
  geom_bar(stat="identity")+
  geom_text(aes(label=Percent.Usable.Data), vjust=0.35, hjust=1.2, color="black", size=2.9)+
  theme(plot.title=element_text(hjust=0.5))+
  coord_flip()+
  labs(title="NOAA Deep Sea Coral Data Portal:\nRanks 4 and 5 Fields of Interest Percent Completion", x="Field Name", y="Percent of Field Filled (%)")+
  scale_fill_discrete(guide = guide_legend(reverse=TRUE), name="Ranking")
```
```{r}
#Ranks 2-3, >0% and <100%
ggplot(data=LessThan100b, aes(x=reorder(FieldName, +Percent.Usable.Data), y=Percent.Usable.Data, fill=factor(Rankings))) +
  geom_bar(stat="identity")+
  geom_text(aes(label=Percent.Usable.Data), vjust=0.35, hjust=1.2, color="black", size=2.5)+
  theme(plot.title=element_text(hjust=0.5))+
  coord_flip()+
  labs(title="NOAA Deep Sea Coral Data Portal:\nRanks 2 and 3 Fields of Interest Percent Completion", x="Field Name", y="Percent of Field Filled (%)")+
  scale_fill_discrete(guide = guide_legend(reverse=TRUE), name="Ranking")
```
```{r}
#Ranks 0-1, >0% and <100%
ggplot(data=LessThan100c, aes(x=reorder(FieldName, +Percent.Usable.Data), y=Percent.Usable.Data, fill=factor(Rankings))) +
  geom_bar(stat="identity")+
  geom_text(aes(label=Percent.Usable.Data), vjust=0.35, hjust=1.2, color="black", size=3.5)+
  theme(plot.title=element_text(hjust=0.5))+
  coord_flip()+
  labs(title="NOAA Deep Sea Coral Data Portal:\nRanks 0 and 1 Fields of Interest Percent Completion", x="Field Name", y="Percent of Field Filled (%)")+
  scale_fill_discrete(guide = guide_legend(reverse=TRUE), name="Ranking")
```

```{r}
glimpse(AllGroups)
```
```{r}
Temperature<-AllGroups %>% filter(-999==Temperature)
table(Temperature$ScientificName)
```
```{r}
Salinity<-AllGroups %>% filter(-999==Salinity)
table(Salinity$ScientificName)
```

```{r}
Oxygen<-AllGroups %>% filter(-999==Oxygen)
table(Oxygen$ScientificName)
```

```{r}
table(AllGroups$SamplingEquipment)
```

```{r}
Temperature2<-AllGroups %>% filter(-999<Temperature)
table(Temperature2$Locality)
```

```{r}
L34.75<-Paramuricea %>% filter(34.5000<latitude)
L34.25<-L34.75 %>% filter(34.0000<latitude)
L33.75<-L34.25 %>% filter(33.5000<latitude)
L33.25<-L33.75 %>% filter(33.0000<latitude)
L32.75<-L33.25 %>% filter(32.5000<latitude)
L32.25<-L32.75 %>% filter(32.0000<latitude)
L31.75<-L32.25 %>% filter(31.5000<latitude)
L31.25<-L31.75 %>% filter(31.0000<latitude)
L30.75<-L31.25 %>% filter(30.5000<latitude)
L30.25<-L30.75 %>% filter(30.0000<latitude)
L29.75<-L30.25 %>% filter(29.5000<latitude)
L29.25<-L29.75 %>% filter(29.0000<latitude)
L28.75<-L29.25 %>% filter(28.5000<latitude)
L28.25<-L28.75 %>% filter(28.0000<latitude)
L27.75<-L28.25 %>% filter(27.5000<latitude)
L27.25<-L27.75 %>% filter(27.0000<latitude)
L26.75<-L27.25 %>% filter(26.5000<latitude)
L26.25<-L26.75 %>% filter(26.0000<latitude)
L25.75<-L26.25 %>% filter(25.5000<latitude)
L25.25<-L25.75 %>% filter(25.0000<latitude)
L24.75<-L25.25 %>% filter(24.5000<latitude)
L24.25<-L24.75 %>% filter(24.0000<latitude)
L23.75<-L24.25 %>% filter(23.5000<latitude)
L23.25<-L23.75 %>% filter(23.0000<latitude)
L22.75<-L23.25 %>% filter(22.5000<latitude)
L22.25<-L22.75 %>% filter(22.0000<latitude)
L21.75<-L22.25 %>% filter(21.5000<latitude)
L21.25<-L21.75 %>% filter(21.0000<latitude)
L20.75<-L21.25 %>% filter(20.5000<latitude)
L20.25<-L20.75 %>% filter(20.0000<latitude)
ParamuriceaLat<-rbind(L20.25,L20.75,L21.25,L21.75,L22.25,L22.75,L23.25,L23.75,L24.25,L24.75,L25.25,L25.75,L26.25,L26.75,L27.25,L27.75,L28.2,L28.75,L29.25,L29.75,L30.25,L30.75,L31.25,L31.75,L32.25,L32.75,L33.25,L33.75,L34.25,L34.75)
```

```{r}
L75.25<-Paramuricea %>% filter(-75.5000<longitude)
L75.75<-L75.25 %>% filter(-76.0000<longitude)
L76.25<-L75.75 %>% filter(-76.5000<longitude)
L76.75<-L76.25 %>% filter(-77.0000<longitude)
L77.25<-L76.75 %>% filter(-77.5000<longitude)
L77.75<-L77.25 %>% filter(-78.0000<longitude)
L78.25<-L77.75 %>% filter(-78.5000<longitude)
L78.75<-L78.25 %>% filter(-79.0000<longitude)
L79.25<-L78.75 %>% filter(-79.5000<longitude)
L79.75<-L79.25 %>% filter(-80.0000<longitude)
L80.25<-L79.75 %>% filter(-80.5000<longitude)
L80.75<-L80.25 %>% filter(-81.0000<longitude)
L81.25<-L80.75 %>% filter(-81.5000<longitude)
L81.75<-L81.25 %>% filter(-82.0000<longitude)
L82.25<-L81.75 %>% filter(-82.5000<longitude)
L82.75<-L82.25 %>% filter(-83.0000<longitude)
L83.25<-L82.75 %>% filter(-83.5000<longitude)
L83.75<-L83.25 %>% filter(-84.0000<longitude)
L84.25<-L83.75 %>% filter(-84.5000<longitude)
L84.75<-L84.25 %>% filter(-85.0000<longitude)
L85.25<-L84.75 %>% filter(-85.5000<longitude)
L85.75<-L85.25 %>% filter(-86.0000<longitude)
L86.25<-L85.75 %>% filter(-86.5000<longitude)
L86.75<-L86.25 %>% filter(-87.0000<longitude)
L87.25<-L86.75 %>% filter(-87.5000<longitude)
L87.75<-L87.25 %>% filter(-88.0000<longitude)
L88.25<-L87.75 %>% filter(-88.5000<longitude)
L88.75<-L88.25 %>% filter(-89.0000<longitude)
L89.25<-L88.75 %>% filter(-89.5000<longitude)
L89.75<-L89.25 %>% filter(-90.0000<longitude)
L90.25<-L89.75 %>% filter(-90.5000<longitude)
L90.75<-L90.25 %>% filter(-91.0000<longitude)
L91.25<-L90.75 %>% filter(-91.5000<longitude)
L91.75<-L91.25 %>% filter(-92.0000<longitude)
L92.25<-L91.75 %>% filter(-92.5000<longitude)
L92.75<-L92.25 %>% filter(-93.0000<longitude)
L93.25<-L92.75 %>% filter(-93.5000<longitude)
L93.75<-L93.25 %>% filter(-94.0000<longitude)
L94.25<-L93.75 %>% filter(-94.5000<longitude)
L94.75<-L94.25 %>% filter(-95.0000<longitude)
L95.25<-L94.75 %>% filter(-95.5000<longitude)
L95.75<-L95.25 %>% filter(-96.0000<longitude)
L96.25<-L95.75 %>% filter(-96.5000<longitude)
L96.75<-L96.25 %>% filter(-97.0000<longitude)
L97.25<-L96.75 %>% filter(-97.5000<longitude)
L97.75<-L97.25 %>% filter(-98.0000<longitude)
ParamuriceaLong<-rbind(L97.75,L97.25,L96.75,L96.25,L95.75,L95.25,L94.75,L94.25,L93.75,L93.25,L92.75,L92.25,L91.75,L91.25,L90.75,L90.25,L89.75,L89.25,L88.75,L88.25,L87.75,L87.25,L86.75,L86.25,L85.75,L85.25,L84.75,L84.25,L83.75,L83.25,L82.75,L82.25,L81.75,L81.25,L80.75,L80.25,L79.75,L79.25,L78.75,L78.25,L77.75,L77.25,L76.75,L76.25,L75.75,L75.25)
```

```{r}
write.csv(Paramuricea, "/Users/17572/Desktop/Paramuricea.csv")
```

```{r}
ParamuriceaLatLong<-read.csv("C:/Users/17572/Desktop/ParamuriceaLatLong.csv")
View(ParamuriceaLatLong)
```

```{r}
Para2875_8825_1<-Paramuricea %>% filter(28.5000<latitude)
Para2875_8825_2<-Paramuricea %>% filter(latitude<29.0000)
Para2875_8825_3<-Paramuricea %>% filter(-88.0000<longitude)
Para2875_8825_4<-Paramuricea %>% filter(latitude< -88.5000)
View(Para2875_8825_4)
ggplot(Para2875_8825_4, aes(x=longitude, y=latitude))+
  geom_point()
```

```{r}
ggplot(Paramuricea, aes(x=longitude, y=latitude))+
  geom_point()
```

```{r}
table(Paramuricea$Locality)
```
```{r}
ParaMC294<-Paramuricea %>% filter(Locality=="MC294")
ParaMC297<-Paramuricea %>% filter(Locality=="MC297")
ParaMC344<-Paramuricea %>% filter(Locality=="MC344")
ParaAT357<-Paramuricea %>% filter(Locality=="AT357")
ParaGC852<-Paramuricea %>% filter(Locality=="GC852")
ParaMC506<-Paramuricea %>% filter(Locality=="MC506")
ParaMC036<-Paramuricea %>% filter(Locality=="MC36")
```

```{r}
summary(ParaMC036$latitude)
summary(ParaMC036$longitude)
```
```{r}
AllData2 <- read.csv("C:/Users/17572/Desktop/AllData2.csv")
View(AllData2)
```

```{r}
GOM<-AllData %>% filter(FishCouncilRegion=="Gulf of Mexico")
GOM200<-GOM %>% filter(200<=DepthInMeters)
GOM200Limited<-GOM200 %>% filter(2009<=ObservationYear)
GOM200Limited2<-GOM200Limited %>% filter(ObservationYear<=2011)
glimpse(GOM200Limited2)
```
```{r}
Para2MC294<-GOM200Limited2 %>% filter(Locality=="MC294")
Para2MC297<-GOM200Limited2 %>% filter(Locality=="MC297")
Para2MC344<-GOM200Limited2 %>% filter(Locality=="MC344")
Para2AT357<-GOM200Limited2 %>% filter(Locality=="AT357")
Para2GC852<-GOM200Limited2 %>% filter(Locality=="GC852")
Para2MC5067<-GOM200Limited2 %>% filter(Locality=="MC506/7")
Para2MC036<-GOM200Limited2 %>% filter(Locality=="MC036")
Para2MC118<-GOM200Limited2 %>% filter(Locality=="MC118")
Para2MC203<-GOM200Limited2 %>% filter(Locality=="MC203")
Para2MC388<-GOM200Limited2 %>% filter(Locality=="MC388")
Para2DC583<-GOM200Limited2 %>% filter(Locality=="DC583")
Para2DC673<-GOM200Limited2 %>% filter(Locality=="DC673")
Para2GC140<-GOM200Limited2 %>% filter(Locality=="GC140")
Para2GB299<-GOM200Limited2 %>% filter(Locality=="GB299")
Para2VK906<-GOM200Limited2 %>% filter(Locality=="VK906")
Para2MC751<-GOM200Limited2 %>% filter(Locality=="MC751")
Para2GC354<-GOM200Limited2 %>% filter(Locality=="GC354")
Para2GB535<-GOM200Limited2 %>% filter(Locality=="GB535")
Para2AT047<-GOM200Limited2 %>% filter(Locality=="AT047")
Para2GC246<-GOM200Limited2 %>% filter(Locality=="GC246")
Para2MC159203<-GOM200Limited2 %>% filter(Locality=="MC159/203")
Para2GC388<-GOM200Limited2 %>% filter(Locality=="GC388")
```

```{r}
table(GOM200Limited2$Locality)
```


